Text as Policy: \\ Measuring Policy Similarity through Bill Text Reuse

### 2016-09-23 manuscript/main.tex
finished updating validation sections

Figure \ref{fig:ncsl_prec_rec} displays the performance of the alignment score
in predicting if two bills are in the same NCSL table. We present
precision---the proportion of bill pairs with a given alignment score that
exceed the threshold on the $x$-axis that are in the same NCSL table, and
recall---the proportion of same-NCSL-table pairs that exceed a given alignment
score threshold. We see very high precision when setting the threshold to
relatively high scores ($>100$). Recall is low at thresholds that produce
reasonable precision (above 100), but that is expected for our case, as
(1) the introduction of similar policies in bills in tow different states is a
rare event, and relatedly, (2) the appearance of two bills in the same NCSL
table is a relatively rare event (8\% in the current analysis); and classifier
recall is notoriously low in rare event data \citep{weiss2000learning}---even
commonly approaching zero, as in our case \citep{weiss2004mining}. Our results
suggest that the presence of a large alignment score between bills is an
effective indicator of policy similarity.

@@

In order to investigate this pattern more closely, we additionally calculate
quantile regressions for the relationship between the alignment score and the
ideological distance. Figure \ref{fig:quantile_regression} displays the
coefficients from quantile regressions on a sequence of quantiles from the
median to the 0.995th quantile. Confidence intervals are calculated by resampling bills, which represents an implementation of the clustered nonparametric bootstrap \citet[see e.g.][]{harden2011bootstrap}. Coefficients significant at the 95\% level are displayed in black, insignificant coefficients are grey. We see that there is only a very weak relationship between the ideological similarity of bill sponsors and the median alignment scores between bills. However, as the quantile we model increases we see that the relationship grows strong and negative in magnitude, and is statistically significant. These results both validate the use of text reuse as a measure of policy similarity, and reinforce the high precision and low recall nature of text reuse as a measure of policy similarity.

>>>>

Figure \ref{fig:ncsl_prec_rec} displays the performance of the alignment score
in predicting if two bills are in the same NCSL table. We present
precision---the proportion of bill pairs with a given alignment score that
exceed the threshold on the $x$-axis that are in the same NCSL table, and
recall---the proportion of same-NCSL-table pairs that exceed a given alignment
score threshold. We see very high precision when setting the threshold to
relatively high scores ($>100$). Recall is low at thresholds that produce
reasonable precision (above 100), but that is expected for our case, as
(1) the introduction of similar policies in bills in tow different states is a
rare event, and relatedly, (2) the appearance of two bills in the same NCSL
table is a relatively rare event (8\% in the current analysis); and classifier
recall is notoriously low in rare event data \citep{weiss2000learning}---even
commonly approaching zero, as in our case \citep{weiss2004mining}. Our results
suggest that the presence of a large alignment score between bills is an
effective indicator of policy similarity. {\bf FRIDO, I DON"T SEE ANYTHING ABOUT THE ADDITIONAL COMPARISONS YOU HAVE DONE HERE. WE DON'T REALLY PROVIDE THE READER WITH A BASELINE FOR COMPARISON HERE. WOULD YOU CALCULATE THE AUCPR OF OUR CLASSIFIER VS A RANDOM CLASSIFIER USING THE PRROC R PACKAGE? ALSO ADD THE VALUE USING THE COSINE SIMILARITY}

@@

In order to investigate this pattern more closely, we additionally calculate
quantile regressions for the relationship between the alignment score and the
ideological distance. In a quantile regression, the dependent variable is the value of the predicted quantile of the distribution of the dependent variable conditional on the independent variables (e.g., the predicted median for median regression with the quantile set to 0.50 \citep{harden2011linear}). Figure \ref{fig:quantile_regression} displays the
coefficients from quantile regressions on a sequence of quantiles from the
median to the 0.995th quantile. Confidence intervals are calculated by resampling bills, which represents an implementation of the clustered nonparametric bootstrap \citet[see e.g.][]{harden2011bootstrap}. Coefficients significant at the 95\% level are displayed in black, insignificant coefficients are grey. We see that there is only a very weak relationship between the ideological similarity of bill sponsors and the median alignment scores between bills. However, as the quantile we model increases we see that the relationship grows strong and negative in magnitude, and is statistically significant. These results both validate the use of text reuse as a measure of policy similarity, and reinforce the high precision and low recall nature of text reuse as a measure of policy similarity.
